Numerical Investigation of Stochastic and Determininstic Upscaling Methods for Permeability Fields; Using SVD

### 2018-03-07 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
Solving reference/citation issue

% Template article for Elsevier's document class `elsarticle'
% with harvard style bibliographic references
% SP 2008/03/01
%
%
%
% $Id: elsarticle-template-harv.tex 4 2009-10-24 08:22:58Z rishi $
%
%
\documentclass[preprint,authoryear,12pt]{elsarticle}

@@

Furthermore, due to limitations in computing resources, for simulations with very fine grids it is neither efficient nor possible to obtain exact values of geological properties at all points in the domain \citep[\ie scale problems,][for further details]{Renard_1997} \cite{miller_1998} \citet{chen_2006}. This is particularly true for large geological domains which span several kilometres. Additionally, it is not possible to obtain reliable and accurate spatial information about geological properties throughout the domain ({\it i.e.}, uncertainty problems). It is possible to overcome these challenges by upscaling. Upscaling techniques solve both problems by replacing discrete geological and fluid property values of detailed high resolution domains with coarse descriptions (low resolution) of these properties \cite{Vereecken_2007}. And upscaling techniques which best preserve the statistical properties and flow dynamics behaviour of the high resolution domain gives the best representation of the heterogeneous property.

>>>>

% Template article for Elsevier's document class `elsarticle'
% with harvard style bibliographic references
% SP 2008/03/01
%
%
%
% $Id: elsarticle-template-harv.tex 4 2009-10-24 08:22:58Z rishi $
%
%
%\documentclass[preprint,authoryear,12pt]{elsarticle}
\documentclass[preprint,12pt]{elsarticle}

@@

Furthermore, due to limitations in computing resources, for simulations with very fine grids it is neither efficient nor possible to obtain exact values of geological properties at all points in the domain (\ie scale problems) \cite{Renard_1997} \cite{miller_1998} \cite{chen_2006}. This is particularly true for large geological domains which span several kilometres. Additionally, it is not possible to obtain reliable and accurate spatial information about geological properties throughout the domain ({\it i.e.}, uncertainty problems). It is possible to overcome these challenges by upscaling. Upscaling techniques solve both problems by replacing discrete geological and fluid property values of detailed high resolution domains with coarse descriptions (low resolution) of these properties \cite{Vereecken_2007}. And upscaling techniques which best preserve the statistical properties and flow dynamics behaviour of the high resolution domain gives the best representation of the heterogeneous property.
